---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(readr)
library(stringr)
```

```{r}
trips_gdrive %>% count(`Parent Brand`, Retailer)
```


```{r}
trips_gdrive %>% count(Retailer, `Parent Brand`) %>%
  arrange(`Parent Brand`, desc(n)) 
```

```{r}
num_HH <- n_distinct(trips_gdrive$`User ID`)
num_HH
```

3. Top Buying Rate
```{r}
num_HH <- n_distinct(trips_gdrive$`User ID`)
trips_gdrive %>%
  mutate(itemDollars = as.integer(str_sub(`Item Dollars`, 2, -1))) %>%
  mutate(total_spend = itemDollars) %>%
  group_by(`Parent Brand`) %>%
  summarise(buyrate = sum(total_spend/num_HH)) %>%
  arrange(desc(buyrate))
```
1 Strongest Affinity

```{r, eval=FALSE}
trips_gdrive %>% 
  group_by(`User ID`, `Parent Brand`) %>%
  mutate(itemDollars = as.integer(str_sub(`Item Dollars`, 2, -1))) %>%
  mutate(total_spend = itemDollars * `Item Units`) %>%
  group_by(`User ID`, `Parent Brand`) %>%
  summarise(totals = sum(total_spend))
```

# Brand Affinity
```{r}
trips_gdrive %>%
  count(`Parent Brand`, Retailer) %>%
  group_by(Retailer) %>%
  mutate(percent_by_retailer = n/sum(n)*100) %>% 
  group_by(`Parent Brand`) %>%
  arrange(`Parent Brand`, percent_by_retailer) %>%
  mutate(retailer_rank = row_number()) %>%
  ggplot() + 
  geom_point(mapping = aes(x = `Parent Brand`, y = Retailer,
                           color = retailer_rank, 
                           size = percent_by_retailer))
```

```{r}
trips_gdrive %>%
  count(`Parent Brand`, Retailer) %>% View()
```

Do duplicates matter? What is the percentage that item count > 1? 
```{r}
trips_gdrive %>%
  count(`Item Units` == 1)
```
Ok. Since multiples (Item Units > 1) only account for 30% of the purchases, I will ignore those. They are more noise than signal.

I also looked to see if they were duplicate trip IDs, which would denote a person buying more than one brand per trip. 

This happened only on a small scale so again, this will be labeled as noise. 

To determine brand affinity, I will define it from the perspective of 'if I am going to x retailer, what brand am I most likely to purchase?' And then I will look at each brand and return the store with which they contribute to the largest slice of sales. There are many angles I could use to measure brand strength (number of dollars, number of units sold, number of unique users). But I will use trips since I like to understand brand affinity from the perspective of each time a person goes out to buy something at a retailer, which brand will they likely purchase. 

Percent of sales by store, trips not item units (get to that later)
```{r}
trips_gdrive %>%
  count(Retailer, `Parent Brand`) %>%
  group_by(Retailer) %>%
  mutate(percent = n/sum(n)) %>% 
  arrange(`Parent Brand`, desc(percent))
```

Counts
```{r}
trips_gdrive %>%
  count(Retailer, `Parent Brand`) %>%
  arrange(`Parent Brand`, desc(n))
```


```{r}
trips_gdrive %>%
  count(`Retailer`) %>% arrange(desc(n))
```
This shows that Walmart has the most trips of any of the stores...something to keep in mind. 
